Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2018-03-18 paper.tex
n
from michael

We developed a modified version of the Morpheus software for bottom-up spectral database searching\citep{Wenger_2013} that we call MetaMorpheus, which integrates the database search procedure with spectral calibration and the enhanced G-PTM-D workflow.
MetaMorpheus is open-source and freely available at \url{https://github.com/smith-chem-wisc/MetaMorpheus}.
MetaMorpheus heavily utilizes an auxiliary library called mzLib, which is a vast library of software tools for analyzing and processing mass spectral data.
mzLib can be found at \url{https://github.com/smith-chem-wisc/mzLib}.

@@

The results of a multi-notch search are assessed using notch-specific FDRs, computed individually for each notch, similarly to MSFragger.
It is important to note that there exist post-processing tools that would push identifications with unknown mass shifts and large numbers of missed cleavages down the list, such as the PeptideProphet extended mass model.

@@

The following supplementary information is available:
\begin{itemize}
  \item Table S1: The complete list of modifications used for enhanced G-PTM-D
  \item Document S1: A brief description of the calibration methodology
  \item Document S2: A 
\end{itemize}

>>>>

We developed a modified version of the Morpheus software for bottom-up spectral database searching\citep{Wenger_2013} that we call MetaMorpheus, which integrates the database search procedure with spectral calibration and the enhanced G-PTM-D workflow.
MetaMorpheus is open-source and freely available at \url{https://github.com/smith-chem-wisc/MetaMorpheus}.
It has attractive properties like Morpheus, such as the ability of running large-scale search tasks on memory-restricted machines.
MetaMorpheus heavily utilizes an auxiliary library called mzLib, which is a vast library of software tools for analyzing and processing mass spectral data.
mzLib can be found at \url{https://github.com/smith-chem-wisc/mzLib}.

@@

The results of a multi-notch search are assessed using notch-specific FDRs, computed individually for each notch, similarly to MSFragger.
MetaMorpheus users interested in further downstream analysis using Percolator can use the pre-formatted Percolator output, which is a tab-delimited file with the file extension \texttt{"forPercolator.tsv"}.
It is important to note that there exist post-processing tools that would push identifications with unknown mass shifts and large numbers of missed cleavages down the list, such as the PeptideProphet~\cite{Ma2012} extended mass model.

Protein-level inference in MetaMorpheus uses all available observed peptides, including PTM-containing peptides. A minimal list of proteins to explain the observed set of peptides is constructed.
Briefly, peptides that could only be a digestion product of one protein in the database ("unique peptides") are used to construct an initial protein set, and any peptide that could be a digestion product of this initial set is associated with those protein(s) and removed from the pool of unassigned peptides.
The remaining unassigned peptides are assigned to proteins using the greedy algorithm.
Proteins with identical peptide sets are grouped. Protein group FDR is estimated with the top-picked method.
In this approach, each protein is paired with its reversed decoy. The PSM with the higher notch q-value (or lower score, in the case of a tie) is retrieved for each protein in the target-decoy pair.
The protein associated with this PSM is considered the lower-quality hit of the pair.
The protein group containing this protein is removed from the protein group set.
Protein groups are then ranked by the notch q-value of their best PSM, and protein q-value is calculated as the number of decoys divided by the number of targets in the ranked list.

@@

The following supplementary information is available:
\begin{itemize}
  \item Table S1: The complete list of modifications used for enhanced G-PTM-D
  \item Document S1: A brief description of the calibration methodology
\end{itemize}

### 2018-03-18 supportingInfo.tex
from michael

\begin{enumerate}
\item \textbf{Table S1} The complete list of modifications used for enhanced G-PTM-D\\
      See Excel file
\item \textbf{Document S1}   A brief description of the calibration methodology      \hfill      Page S-1
\item \textbf{Document S2}         \hfill      Page S-2
\end{enumerate}

@@

If a pre-calibrated file is given as an input, no changes are made. This is due to the fact that the calibration procedure only accepts changes if a test database search results show improvement.

>>>>

\begin{enumerate}
\item \textbf{Table S1} The complete list of modifications used for enhanced G-PTM-D\\
      See Excel file
\item \textbf{Document S1}   A brief description of the calibration methodology      \hfill      Page S-1
\end{enumerate}

@@

If a well-calibrated file is given as an input, no changes are made. This is because the calibration procedure only accepts changes if a test database search results in improvement.
